Statically Typed String Sanitation Inside a Python

### 2014-10-03 sanitation-psp14/sanitation-psp14-short.tex
Minor changes.
Adeed a line to sec. 3 per review 2.

\begin{defn}[Definition of \lhead{r}]
The function $\lhead{r}$ is defined in terms of the structure of $r$:
\begin{itemize}[noitemsep]
\item $\lhead{a r'} = a$ where $a \in \Sigma$
\item $\lhead{\epsilon} = \epsilon$
\item $\lhead{r_1 +  r_2}  = \lhead{r_1} + \lhead{r_2}$
\item $\lhead{r*} = \lhead{r}$
\item $\lhead{.} = a_1 + a_2 + ... + a_n$ for all $a_i \in \Sigma$ where $|\Sigma| = n$.
\end{itemize}
\end{defn}

@@

The chief benefit of $\lambdas$ is its safety theorem, which states that any value of
a regular expression type is recognized by the regular expression corresponding to its type.
Our main technical result, stated later in this section, establishes that this property
is preserved under translation into $\lambdap$.

>>>>

\begin{defn}[Definition of \lhead{r}]
The function $\lhead{r}$ is defined in terms of the structure of $r$:
\begin{itemize}[noitemsep]
\item $\lhead{a r'} = a$ where $a \in \Sigma$
\item $\lhead{r_1r_2} = \lhead{r_1}$
\item $\lhead{\epsilon} = \epsilon$
\item $\lhead{r_1 +  r_2}  = \lhead{r_1} + \lhead{r_2}$
\item $\lhead{r*} = \lhead{r}$
\item $\lhead{.} = a_1 + a_2 + ... + a_n$ for all $a_i \in \Sigma$ where $|\Sigma| = n$.
\end{itemize}
\end{defn}

@@

The chief benefit of $\lambdas$ is its security theorem, which states that any value of
a regular expression type is recognized by the regular expression corresponding to its type.
This is beneficial because safe subsets of strings may be characterized by regular expressions.
Our main technical result, stated later in this section, establishes that the security property
is preserved under translation into $\lambdap$.
